New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2022-09-07 paper/paper.Rmd
conclusions mapped out

The @tourr package provides numerous types of tours. An additional function has been constructed that will generate a sequence of projections that will decrease the coordinates for $V_m$ to $\boldsymbol{0}$ and back to the original values. It is applicable for any projection dimension, $d$.

@@

Recap contribution

@@

Maybe extensions for slicing

>>>>

The R package tourr [@tourr] provides numerous types of tours. An additional function, `radial_tour()` has been constructed that will generate a sequence of projections that will decrease the coordinates for $V_m$ to $\boldsymbol{0}$ and back to the original values. It is applicable for any projection dimension, $d$.

@@

This short note has described new technology for manually interacting with tours. The manual control of projection coefficients is most useful for assessing variable importance to perceived structure, but can be generally used for steering a viewer through high-dimensional space. Changing the center of a slice manually enables exploring the space orthogonal to a projection, specifically in the direction of a single variable. This is a new tool, and as shown in the example, when used with the slice tour can very useful for understanding boundaries of classifiers. This is also likely a useful method for examining low-dimensional non-linear manifolds, and also functions of multiple parameters.

Mathematica provided a useful sandbox to experiment with the ideas presented in this paper. Most of the data, though, is first constructed using R, especially the classification boundaries. If new technology for interactive graphics becomes available in R it would be useful to create a tighter coupling of models and visualization to allow exploring and comparing fits.

<!-- Recap contribution

@@

Maybe extensions for slicing-->

### 2022-09-07 paper/paper.tex
conclusions mapped out

The \citet{tourr} package provides numerous types of tours. An
additional function has been constructed that will generate a sequence
of projections that will decrease the coordinates for \(V_m\) to
\(\boldsymbol{0}\) and back to the original values. It is applicable for
any projection dimension, \(d\).

@@

Recap contribution

Other applications

Where else might it be useful to use mathematica

Maybe extensions for slicing

>>>>

The R package tourr \citep{tourr} provides numerous types of tours. An
additional function, \texttt{radial\_tour()} has been constructed that
will generate a sequence of projections that will decrease the
coordinates for \(V_m\) to \(\boldsymbol{0}\) and back to the original
values. It is applicable for any projection dimension, \(d\).

@@

This short note has described new technology for manually interacting
with tours. The manual control of projection coefficients is most useful
for assessing variable importance to perceived structure, but can be
generally used for steering a viewer through high-dimensional space.
Changing the center of a slice manually enables exploring the space
orthogonal to a projection, specifically in the direction of a single
variable. This is a new tool, and as shown in the example, when used
with the slice tour can very useful for understanding boundaries of
classifiers. This is also likely a useful method for examining
low-dimensional non-linear manifolds, and also functions of multiple
parameters.

Mathematica provided a useful sandbox to experiment with the ideas
presented in this paper. Most of the data, though, is first constructed
using R, especially the classification boundaries. If new technology for
interactive graphics becomes available in R it would be useful to create
a tighter coupling of models and visualization to allow exploring and
comparing fits.
